### 2020-07-19 manuscript/explorations/phylobayes_explorations.rmd
incomplete records return NULL rather than throw error
parses unconstrained CAT chains

```{r preliminaries}
  library( tidyverse )
  library( magrittr )

@@

chain = parse_phylobayes_chain("../tests/testthat/example.chain")

@@

categories %>% 
  ggplot() +
  geom_point(aes(x=x, y=y, size=count) ) +
  ggtitle("MDS plot of rate categories") +
  theme_classic()

@@

>>>>

```{r preliminaries}
  library( tidyverse )
  library( magrittr )
  library( gridExtra )

@@

plot_chain = function( pb ){

@@

  gg_mds = 
  categories %>% 
    ggplot() +
    geom_point(aes(x=x, y=y, size=count) ) +
    ggtitle("MDS plot of rate categories") +
    theme_classic()

  gg_rank = 
    categories %>%
    arrange(desc(count)) %>%
    mutate(rank = 1:nrow(categories)) %>%
    ggplot() +
      geom_point(aes(x=rank, y=count) ) +
      ggtitle("Ordered count") +
      theme_classic()

  p = grid.arrange(
  	gg_rank,
  	gg_mds,
  	ncol = 2
  )

  return(p)
}

@@

chain = parse_phylobayes_chain( "../tests/testthat/example.chain" )

plot_chain( pb )

**Figure n60.** Plots for nCAT=60.

chain = parse_phylobayes_chain( "Whelan2017_strict.phy_Poisson_CAT100_Chain_1_last500.chain" )

plot_chain( pb )

**Figure n100.** Plots for nCAT=100.

chain = parse_phylobayes_chain( "Whelan2017_strict.phy_Chain1_last50000.chain" )

plot_chain( pb )

**Figure CAT.** Plots for CAT.
